%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Model Developer} % Job title
    {Darktrace} % Organization
    {Toronto, Canada} % Location
    {May. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research and develop machine learning models to detect adversary activity in the network, cloud and SaaS environments.}
        \item {Maintain 900+ threat models, improving accuracy and fidelity of detections by \~25\% using test-driven development and CI/CD.}
        \item {Develop and maintain analytical tools (fullstack) used to identify statistical trends and malicious activity in global breach data.}
        \item {Research classification methods to improve detections of malicious activity such as DNS Tunelling communications.}
        \item {Simulate cloud and network attack tools and tested malware against the detection system to improve capabilities.}
        \item {Lead development of Cloud and SaaS threat detection models in AWS, Azure, GCP, M365, GSuite, Salesforce, Okta, etc.}
        \item {Train internal teams and supported key strategic customers with model optimization, development, and training.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cyber Security Analyst} % Job title
    {} % Organization
    {} % Location
    {Nov. 2018 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead analyst in Canada and security Subject Matter Expert, supporting strategic technical client engagements in North America.}
        \item {Performed threat hunting exercises on client environments, writing weekly/monthly threat reports with detailed technical analysis.}
        \item {Investigated active compromises and live pen-tests in customer environemnts, compiling incident reports for clients/executives.}
        \item {Maintainer of the Darktrace Python library, a light-weight wrapper library for simple implementation of the Darktrace API.}
        \item {Identified 50+ new IOCs for Darktrace threat intel database from threat hunting exercises and research.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cyber Security Engineer} % Job title
    {} % Organization
    {} % Location
    {Sep. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed integrations and deployments of Darktrace system across Canada for network, virtual, and cloud environments.}
        \item {Traveled weekly to lead onsite technical integrations with security engineers, managers and executives.}
        \item {Developed internal SSH CLI tool to improve workflow, speed and security of accessing internal resources.}
        \item {Contributed to over 30\% growth of the Canadian customer base from proof-of-value customer trials.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Category Management Analyst} % Job title
    {Zebra Technologies} % Organization
    {Missisaugua, Canada} % Location
    {May. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a dynamic Excel (VBA) dashboard to automate monthly analysis reporting of vendor operational and financial risk.}
        \item {Led RFQ/RFP exercise with key vendors to reduce cost on tail-spend of global semiconductor component procurement.}
      \end{cvitems}
    }
    % {      
    %   \begin{cvsubentries}
    %    \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
    %    \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
    %   \end{cvsubentries}
    % }

%---------------------------------------------------------
\end{cventries}
